Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_catalogue.tex
some major changes
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@861 d8b0c59b-6544-0410-94d9-83a5658a058e

\section{Discovery: the marketplace}
\label{sec:discovery}

@@

\begin{itemize}
	\item offers web services as Linked Data;
	\item serves web services wrappers ready-to-consume in any web application;
	\item follows well-known best practices for publishing data on the web;
	\item supports managing its resources via its RESTful API;
	\item supports content negotiation so the different clients may retrieved the information in JSON, RDF/XML, RDF/N3 or a human-readable HTML version;
	\item provices advanced search capabilites, based on the service formal definition and inferences extracted from it;
	\item a SPARQL endpoint to access directly to the data allowing advanced queries;
\end{itemize}

This platform was intented and it is being used as part of the FAST storyboard tool. Others components communicates with it via its RESTful API, but a
That said, The process of publishing a web service requires two steps: (i) generation of the wrapper (see Sec. \ref{sec:wrapping_web_services}, and (ii) creation of the resource in the publishing platform. The creation of the resources is done via the public RESTful API, and the language selected for the input for any operation is JSON. The following is an example of part of a request sent to create a new wrapper into the platform:

\begin{listing}
\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonService.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "description": {"en-gb": "Amazon web service"},
  "label": {"en-gb": "Amazon web service"},
  "preconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?item 
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "postconditions": [
    ...
  ],
  ...
\end{verbatim}
\label{lis:json_request}
\end{listing}

The architecture, as presented in the Figure \ref{fig:}, comprises a RDF store used for persistence, a business layer dealing with the model and reasoning, and public façade providing the core functionality as a RESTful API, and a SPARQL endpoint accessing directly the RDF store. This presentation layer is aimed to interact with the FAST Gadget Visual Storyboard, or any other third-party application.

@@

The business logic layer contains all the domain-specific processing and reasoning. It provides functions to interact with all the elements of the domain model specified in \cite{sec:model}, acting as a mediator between the public RESTful API and the persistence layer.

The persistence layer provides an API to work with a standard set of objects representing the model. The interaction with the underlying RDF store is made via RDF2Go, an abstraction over triple (and quad) stores, which allows to program against rdf2go interfaces and choose any the RDF store implementation. This allows having a completely extensible and configurable framework for storage mechanisms, inferencers, RDF file formats, query result formats and query languages...

How to publish (RESTful app, anyone can create a wrapper and publish it)

How to browse: will allow users to go through the given domains (ontologies) and concepts, and will explain how to find the services they want (operation Find of the catalogue) => how the recommendation/reasoning works

It offers the wrapped web services as linked data and has an open sparql endpoint, allowing other developers to create applications on top of it...

>>>>

\section{Discovery: web services publishing platform}
\label{sec:discovery}

@@

\begin{itemize}
  \item allows functional discovery through web services pre and postconditions;
	\item serves web services wrappers ready-to-consume in any web application;
	\item provices advanced search capabilites, based on the service formal definition and inferences extracted from it;
	\item supports managing its resources via its RESTful API;
	\item a SPARQL endpoint to access directly to the data allowing advanced queries;
	\item offers web services as Linked Data;
	\item follows well-known best practices for publishing data on the web;
	\item supports content negotiation so the different clients may retrieved the information in JSON, RDF/XML, RDF/N3 or a human-readable HTML version;
\end{itemize}

This platform was intented and it is being used as part of the FAST storyboard tool, and it communicates with others components through its RESTful API, using JSON for the input of the requests. This paper will focus on the functionality regarding web services publication and discovery, and the process to publish any third-party web service into the platform. This process requires two steps: (i) generation of the wrapper (see Sec. \ref{sec:wrapping_web_services}, and (ii) creation of the resource in the publishing platform. The following is an example of part of a request sent to create a new wrapper into the platform (for the sake of clarity, some parts of the request have been ommitted, but the main idea is shown):

\begin{listing}
\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonSearch.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "description": {"en-gb": "Amazon web service - Search"},
  "label": {"en-gb": "Amazon search"},
  "actions": [{
    "name": "filter",
    "preconditions": [[{
      "id": "item",
      "label": {"en-gb": "Ebay List"},
      "pattern": "?item
                  http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                  http://aws.amazon.com/AWSECommerceService#Item",
      "positive": true
  }]],
  "postconditions": [
    ...
  ],
  ...
\end{verbatim}
\label{lis:json_request}
\end{listing}

The enriched search capabilities are supported by the definition of pre and postcondition. It allows to define the inputs and outputs of the services using concepts from any ontology, and find web services which match and hence is able to communicate with other web services or building block. The concepts of pre/postconditions were highly influenced by WSMO \cite{roman2005}, make it simpler and implemented in RDFS for a better performance. The model used to define the web service wrappers and the ontology created are detailed in Section~\ref{ssec:ontology}.

\subsection{Platform architecture}
\label{ssec:architecture}

The architecture comprises a RDF store used for persistence, a business layer dealing with the model and reasoning, and public façade providing the core functionality as a RESTful API, and a SPARQL endpoint accessing directly the RDF store. This presentation layer is aimed to interact with the FAST Gadget Visual Storyboard, or any other third-party application.

@@

The business logic layer contains all the domain-specific processing and reasoning. It provides functions to interact with all the elements of the domain model specified in \cite{ssec:ontology}, acting as a mediator between the public RESTful API and the persistence layer.

The persistence layer provides an API allowing to work with a standard set of objects representing the model. The interaction with the underlying RDF store is made via RDF2Go, an abstraction over triple (and quad) stores, which allows to program against rdf2go interfaces and choose any the RDF store implementation. This allows having a completely extensible and configurable framework for storage mechanisms, inferencers, RDF file formats, query result formats and query languages.
